\chapter{Project Assumptions}\label{ch:assumptions}
\section{Problem Statement}\label{sec:assumptions:problem}
As children's productivity declines nowadays and current methods of boosting it are not sufficient any longer, parents need a simple tool to manage their tasks and reward them.


\section{Target Group}\label{sec:assumptions:target}
\subsection{Children}\label{subsec:assumptions:target:children}
The primary target group are children. Their age range is between 5 and 12. Younger children might not be self-aware and independent enough to complete tasks. The older ones might find the concept boring and childish.

\subsection{Parents}\label{subsec:assumptions:target:parents}
As a natural consequence, the other target group are parents. The age range restriction is unnecessary; however, they should be comfortable using mobile devices.


\section{Core Features}\label{sec:assumptions:features}
Main features of the application should be:
\begin{itemize}
\item Parents being able to set up an account.
\item Parents being able to manage multiple children.
\item Parents being able to manage children's tasks and rewards.
\item Children being able to view their tasks and rewards. 
\end{itemize}


\section{Platform}\label{sec:introduction:platform}
The application should be targeted for mobile devices; however, with consideration of a future expansion to other platforms (web in particular). Target devices are smartphones with Android operating system, nevertheless, it would be desirable that it could be easily converted to iOS and tablets.


\section{Project Glossary}\label{sec:assumptions:glossary}
// TODO: Update if needed
\begin{itemize}
    \item \textit{Parent} - The person responsible for children as well as managing their tasks and rewards.
    \item \textit{Child} - The person designated by the parent to be a recipient of tasks and rewards.
    \item \textit{Task} - A piece of work defined by a parent to be undertaken by a child.  
    \item \textit{Reward} - Something given in exchange for completed tasks, not necessarily a material thing.
    \item \textit{Point} - A numeric score assigned to every task and every reward. It is defined as an asset in case of the former and as a cost in case of the latter.
    \item \textit{Artifact} (also \textit{Gamification Artifact}) - Game design element that attempts to invoke certain motivations, e.g. \textit{Task}, \textit{Reward}, \textit{Point}.
    \item \textit{User's (Child's / Parent's) perspective} - layout and functionality corresponding with the user's role (a parent or a child). 
    \item \textit{Device} - any device that runs the application.
    \item \textit{Device Belonging} - device assignment corresponding with the current user's role (a parent or a child). It defines the user's perspective.
    \item \textit{Account / Parent's Account} - an account identified by email and password, one per family, usually belonging to a parent; it is an administrative unit and can manage multiple profiles.
    \item \textit{Profile / Child's Profile} - a separate unit with its own points, tasks and rewards, usually belonging to a child; it belongs to exactly one account.
\end{itemize}
