\UseCaseTable{1}
{view-tasks}
{View Tasks}
{Child}
{A Child wants to see their tasks.}
{\begin{enumerate} % Preconditions
    \item A child's profile has been chosen.
\end{enumerate}}
{\begin{enumerate} % Postconditions
    \item The Child's tasks are displayed.
\end{enumerate}}
{\begin{enumerate} % Base flow
    \item The Child navigates to a tasks screen.
    \item If there are tasks assigned to the child, they are displayed.
\end{enumerate}}
{\begin{enumerate} % Alternative flow
[label=2.\alph*.]
    \item If there are no tasks assigned to the child, an information about it is displayed instead.
\end{enumerate}}
{-} % Exceptions
{-} % Extensions


\UseCaseTable{2}
{view-profile}
{View Profile}
{Child}
{A Child wants to see their profile information.}
{\begin{enumerate} % Preconditions
    \item A child's profile has been chosen.
\end{enumerate}}
{\begin{enumerate} % Postconditions
    \item The Child's profile information is displayed.
\end{enumerate}}
{\begin{enumerate} % Base flow
    \item The Child navigates to a profile screen.
    \item The profile information is displayed.
\end{enumerate}}
{-} % Alternative flow
{-} % Exceptions
{-} % Extensions


\UseCaseTable{3}
{view-rewards}
{View Rewards}
{Child}
{A Child wants to see their rewards.}
{\begin{enumerate} % Preconditions
    \item A child's profile has been chosen.
\end{enumerate}}
{\begin{enumerate} % Postconditions
    \item The Child's rewards are displayed.
\end{enumerate}}
{\begin{enumerate} % Base flow
    \item The Child enters a rewards screen.
    \item If there are rewards assigned to the child, they are displayed.
\end{enumerate}}
{\begin{enumerate} % Alternative flow
[label=2.\alph*.]
    \item If there are no rewards assigned to the child, an information about it is displayed instead.
\end{enumerate}}
{-} % Exceptions
{-} % Extensions


\UseCaseTable{4}
{filter-tasks}
{Filter Tasks}
{Child}
{A Child wants to filter the displayed tasks.}
{\begin{enumerate} % Preconditions
    \item A child's profile has been chosen.
    \item A tasks screen has been entered.
\end{enumerate}}
{\begin{enumerate} % Postconditions
    \item The displayed Child's tasks are filtered according to the filter choice. 
\end{enumerate}}
{\begin{enumerate} % Base flow
    \item The Child chooses a filter from a list of available filters.
    \item The displayed tasks are filtered accordingly.
\end{enumerate}}
{\begin{enumerate} % Alternative flow
[label=2.\alph*.]
    \item If there are no tasks with the assigned filter, an information about it is displayed instead.
\end{enumerate}}
{-} % Exceptions
{-} % Extensions


\UseCaseTable{5}
{filter-rewards}
{Filter Rewards}
{Child}
{A Child wants to filter the displayed rewards.}
{\begin{enumerate} % Preconditions
    \item A child's profile has been chosen.
    \item A rewards screen has been entered.
\end{enumerate}}
{\begin{enumerate} % Postconditions
    \item The displayed Child's rewards are filtered according to the filter choice. 
\end{enumerate}}
{\begin{enumerate} % Base flow
    \item The Child chooses a filter from a list of available filters.
    \item The displayed rewards are filtered accordingly.
\end{enumerate}}
{\begin{enumerate} % Alternative flow
[label=2.\alph*.]
    \item If there are no rewards with the assigned filter, an information about it is displayed instead.
\end{enumerate}}
{-} % Exceptions
{-} % Extensions


\UseCaseTable{6}
{add-child}
{Add Child}
{Parent}
{A Parent wants to add a new child's profile.}
{\begin{enumerate} % Preconditions
    \item A parent's perspective has been enabled.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item A new child's profile is added and visible on the children's profiles list.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item The Parent clicks an \say{add child} button.
   \item The Mobile Application displays an \say{add child} form.
   \item The Parent fills in the form with the new child's profile data and confirms it.
   \item The Mobile Application sends the data to the Database Service and updates its children list.
   \item The new child's profile is displayed on the children's profiles list.
\end{enumerate}}
{-}% Alternative flow
{\begin{enumerate} % Exceptions
[label=3.\alph*.]
    \item If the input data is not compliant with the validation rules, the system displays an error message.
\end{enumerate}}
{-} % Extensions


\UseCaseTable{7}
{add-task}
{Add Task}
{Parent}
{A Parent wants to add a task for their child.}
{\begin{enumerate} % Preconditions
    \item A parent's perspective has been enabled.
    \item A child's profile has been chosen.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item A new child's task is added and visible on the child's task screen.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item The Parent clicks an \say{add task} button.
   \item The Mobile Application displays an \say{add task} form.
   \item The Parent fills in the form with the new task's data and confirms it.
   \item The Mobile Application sends the data to the Database Service and updates its tasks list.
   \item The new task is displayed on the tasks list.
\end{enumerate}}
{-}% Alternative flow
{\begin{enumerate} % Exceptions
[label=3.\alph*.]
    \item If the input data is not compliant with the validation rules, the system displays an error message.
\end{enumerate}}
{-} % Extensions


\UseCaseTable{8}
{add-reward}
{Add Reward}
{Parent}
{A Parent wants to add a reward for their child.}
{\begin{enumerate} % Preconditions
    \item A parent's perspective is enabled.
    \item A child's profile is chosen.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item A new child's reward is added and visible on the child's task screen.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item The Parent clicks an \say{add reward} button.
   \item The Mobile Application displays an \say{add reward} form.
   \item The Parent fills in the form with the new reward's data and confirms it.
   \item The Mobile Application sends the data to the Database Service and updates its rewards list.
   \item The new reward is displayed on the rewards list.
\end{enumerate}}
{-}% Alternative flow
{\begin{enumerate} % Exceptions
[label=3.\alph*.]
    \item If the input data is not compliant with the validation rules, the system displays an error message.
\end{enumerate}}
{-} % Extensions


\UseCaseTable{9}
{edit-task}
{Edit Task}
{Parent}
{A Parent wants to edit their child's task.}
{\begin{enumerate} % Preconditions
    \item A parent's perspective has been enabled.
    \item A child's profile has been chosen.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item An edited task has its details or state changed.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item The Parent long-presses a chosen task from the tasks list.
   \item The Mobile Application displays an \say{edit task} form with the task data pre-filled.
   \item The Parent amends the data and confirms the changes.
   \item The Mobile Application sends the data to the Database Service and updates its tasks list.
   \item The task with edited data is displayed on the tasks list.
\end{enumerate}}
{\begin{enumerate} % Alternative flow
    \item[1.a.] The Parent taps a chosen task from the tasks list.
    \item[2.a.] The Parent confirms changing the task state.
\end{enumerate}
}
{\begin{enumerate} % Exceptions
    \item[3.b.] If the input data is not compliant with the validation rules, the system displays an error message.
\end{enumerate}}
{-} % Extensions


\UseCaseTable{10}
{edit-reward}
{Edit Reward}
{Parent}
{A Parent wants to edit their child's reward.}
{\begin{enumerate} % Preconditions
    \item A parent's perspective has been enabled.
    \item A child's profile has been chosen.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item An edited reward has its details or state changed.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item The Parent long-presses a chosen reward from the rewards list.
   \item The Mobile Application displays an \say{edit reward} form with the reward data pre-filled.
   \item The Parent amends the data and confirms the changes.
   \item The Mobile Application sends the data to the Database Service and updates its rewards list.
   \item The reward with edited data is displayed on the rewards list.
\end{enumerate}}
{\begin{enumerate} % Alternative flow
    \item[1.a.] The Parent taps a chosen reward from the rewards list.
    \item[2.a.] The Parent confirms changing the reward state.
\end{enumerate}
}
{\begin{enumerate} % Exceptions
    \item[3.b.] If the input data is not compliant with the validation rules, the system displays an error message.
\end{enumerate}}
{-} % Extensions


\UseCaseTable{11}
{edit-child}
{Edit Child}
{Parent}
{A Parent wants to edit their child's profile.}
{\begin{enumerate} % Preconditions
    \item A parent's perspective has been enabled.
    \item A child's profile has been chosen.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item An edited child's profile has its details changed.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item The Parent navigates to the child's profile screen and clicks an \say{edit child} button.
   \item The Mobile Application displays an \say{edit child} form with the child's profile data pre-filled.
   \item The Parent amends the data and confirms the changes.
   \item The Mobile Application sends the data to the Database Service and updates its child's profile data.
   \item The child's profile with edited data is displayed on the children's profiles list.
\end{enumerate}}
{-} % Alternative flow
{\begin{enumerate} % Exceptions
    \item[3.a.] If the input data is not compliant with the validation rules, the system displays an error message.
\end{enumerate}}
{-} % Extensions


\UseCaseTable{12}
{delete-task}
{Delete Task}
{Parent}
{A Parent wants to remove their child's task.}
{\begin{enumerate} % Preconditions
    \item A parent's perspective has been enabled.
    \item A child's task edit form has been entered.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item A deleted task is available neither for the child, nor the parent.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item The Parent clicks a \say{delete task} button and confirms the action.
   \item The Mobile Application sends the delete request to the Database Service and updates its child's tasks list.
   \item The deleted task is not displayed on the tasks list.
\end{enumerate}}
{-} % Alternative flow
{-} % Exceptions
{-} % Extensions


\UseCaseTable{13}
{delete-reward}
{Delete Reward}
{Parent}
{A Parent wants to remove their child's reward.}
{\begin{enumerate} % Preconditions
    \item A parent's perspective has been enabled.
    \item A child's reward edit form has been entered.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item A deleted reward is available neither for the child, nor the parent.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item The Parent clicks a \say{delete task} button and confirms the action.
   \item The Mobile Application sends the delete request to the Database Service and updates its child's tasks list.
   \item The deleted reward is not displayed on the rewards list.
\end{enumerate}}
{-} % Alternative flow
{-} % Exceptions
{-} % Extensions

\UseCaseTable{14}
{delete-child}
{Delete Child}
{Parent}
{A Parent wants to remove their child's profile.}
{\begin{enumerate} % Preconditions
    \item A parent's perspective has been enabled.
    \item A child's profile edit form has been entered.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item A deleted child's profile is available neither for the child, nor the parent.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item The Parent clicks a \say{delete child} button and confirms the action.
   \item The Mobile Application sends the delete request to the Database Service for all the child's tasks, rewards along with the child's profile and updates its children's profiles list.
   \item The deleted child's profile is not displayed on the children's profiles list.
\end{enumerate}}
{-} % Alternative flow
{-} % Exceptions
{-} % Extensions

\UseCaseTable{15}
{choose-child}
{Choose Child}
{Parent}
{A Parent wants to choose the child's profile to start managing it.}
{\begin{enumerate} % Preconditions
    \item A parent's perspective has been enabled.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item A child's profile is selected and can be managed.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item The Parent clicks a \say{child profile} element on the children's profiles list.
   \item The Mobile Application navigates to the child's profile screen.
\end{enumerate}}
{-} % Alternative flow
{-} % Exceptions
{\begin{enumerate} % Extensions
   \item \textit{Add Task} (Table \ref{tab:use-case:add-task})
   \item \textit{Add Reward} (Table \ref{tab:use-case:add-reward})
   \item \textit{Edit Task} (Table \ref{tab:use-case:edit-task})
   \item \textit{Edit Reward} (Table \ref{tab:use-case:edit-reward})
   \item \textit{Edit Child} (Table \ref{tab:use-case:edit-child})
   \item \textit{Delete Task} (Table \ref{tab:use-case:delete-task})
   \item \textit{Delete Reward} (Table \ref{tab:use-case:delete-reward})
   \item \textit{Delete Child} (Table \ref{tab:use-case:delete-child})
\end{enumerate}}

\UseCaseTable{16}
{sign-in}
{Sign in}
{Parent}
{A Parent wants to access their account.}
{\begin{enumerate} % Preconditions
    \item A Parent is not logged in.
    \item A device belonging choice screen has been entered.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item A parent is logged in and can access their account.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item The Parent chooses the \textit{parent} device belonging.
   \item The Mobile Application navigates to the register screen.
   \item The Parent clicks a \textit{Sign in instead} button.
   \item The Mobile Application navigates to the login screen.
   \item The Parent fills in the login data and confirms it.
   \item The Mobile Application sends the data to the Authentication Service.
   \item The Authentication Service confirms the data is correct.
   \item The Mobile Application saves user's authentication token and displays the parent's perspective.
\end{enumerate}}
{\begin{enumerate} % Alternative flow
    \item[1.a.] The Parent chooses the \textit{child} device belonging.
    \item[2.a.] The flow continues from point no. 4 of the base flow.
\end{enumerate}}
{\begin{enumerate} % Exceptions
    \item[3.b.] The Authentication Service denies the data is correct.
    \item[4.b.] The Mobile Application displays an error message.
\end{enumerate}}
{-} % Extensions

\UseCaseTable{17}
{sign-out}
{Sign out}
{Parent}
{A Parent wants to stop accessing their account.}
{\begin{enumerate} % Preconditions
    \item A Parent is logged in.
    \item A settings screen has been entered.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item A parent is logged out and cannot access their account.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item The Parent clicks \textit{Sign out} button.
   \item The Mobile Application sends the \textit{sign out} request to the Authentication Service
   \item The Mobile Application navigates to the 
\end{enumerate}}
{-}% Alternative flow
{-}
{-} % Extensions

\UseCaseTable{18}
{change-device-belonging}
{Change Device Belonging}
{Parent}
{A Parent wants to toggle between the user's perspectives.}
{\begin{enumerate} % Preconditions
    \item A Parent is logged in.
    \item A settings screen has been entered.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item A device belonging is changed.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item If the \textit{parent's} device belonging is chosen, the Parent selects the \textit{child's} device belonging.
   \item The Mobile Application displays an additional child's profile select field.
   \item The Parent chooses a specific child's profile and confirms their choice.
   \item The Mobile Application saves the selected device belonging.
\end{enumerate}}
{\begin{enumerate} % Base flow
    \item[1.a.] If the \textit{child's} device belonging is chosen, the Parent selects the \textit{parent's} device belonging.
    \item[2.a.] The Mobile Application hides the additional child's profile select field.
    \item[3.a.] The Parent confirms their choice.
\end{enumerate}
\midrule
\begin{enumerate}
    \item[1.b.] If the \textit{child's} device belonging is chosen, the Parent selects another child in the child's profile select field.
    \item[2.b.] - 
    \item[3.b.] The Parent confirms their choice.
\end{enumerate}}% Alternative flow
{-} % Exceptions
{-} % Extensions

\UseCaseTable{19}
{change-settings}
{Change settings}
{Parent}
{A Parent wants to display available settings.}
{\begin{enumerate} % Preconditions
    \item A Parent is logged in.
    \item A children's profiles list screen (in the parent's perspective) or a child's profile screen (in the child's perspective) is entered.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item A settings screen is displayed.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item The Parent clicks a settings button.
   \item The Parent enters their password to authorize settings edition.
   \item The Mobile Application displays screen setting.
\end{enumerate}}
{-} % Alternative flow
{-} % Exceptions
{\begin{enumerate} % Extensions
   \item \textit{Sign out} (Table \ref{tab:use-case:sign-out})
   \item \textit{Change Device Belonging} (Table \ref{tab:use-case:change-device-belonging})
\end{enumerate}}

\UseCaseTable{20}
{sign-up}
{Sign up}
{New User}
{A New User wants to create an account.}
{\begin{enumerate} % Preconditions
    \item The Mobile Application does not have device belonging or login data saved.
\end{enumerate}}
{\begin{enumerate} % Postconditions
   \item A new account is registered, and the New User becomes a Parent.
\end{enumerate}}
{\begin{enumerate} % Base flow
   \item The New User chooses the parent's device belonging.
   \item The Mobile Application saves the device belonging and navigates to the register screen.
   \item The New User enters the new account data and confirms it with a button.
   \item The Mobile Application sends the data to the Authentication Service.
   \item The Authentication Service confirms the data is correct.
   \item The Mobile Application saves user's authentication token and displays the parent's perspective.
\end{enumerate}}
{-} % Alternative flow
{\begin{enumerate} % Exceptions
    \item[5.a.] The Authentication Service denies the data is correct.
    \item[6.a.] The Mobile Application displays an error message.
\end{enumerate}}
{-} % Extensions
